Measurement and Probability in Fuzzy Quantum Theories

### 2017-03-07 prop_iop.tex
prop_iop.tex \section{Contextuality and the Born Rule in Fuzzy Quantum Theories} Updating...

On one hand, the Kochen-Specker theorem is equivalent to non-existence
of quantum cryptodeterministic measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $,
where $\events$ is the set of all projections on a Hilbert space.
On the other hand, if we replace the range by the interval~$\left[0,1\right]$,
Gleason's theorem asserts that every quantum real-valued probability
measure~$\mu:\events\rightarrow\left[0,1\right]$ can be induced
by a density matrix according to the Born rule. These two extreme
cases can be understood in a broader framework of quantum interval-valued
probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$, where
$\mathscr{I}$ is a collection of intervals containing in $\left[0,1\right]$.
When we pick $\mathscr{I}$ as $\left\{ \imposs,\necess\right\} $,
where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$,
there is no quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
by corollary~\ref{cor:Kochen-Specker-IVPM} of the Kochen-Specker
theorem. When the collection of intervals is $\set{\left\{ x\right\} }{x\in\left[0,1\right]}$,
a quantum interval-valued probability measure is well-behaved as a
usual quantum real-valued probability measure does.

Given any sub-event space~$\events'\subseteq\events$, in order to
qualify how well-behaved a quantum interval-valued probability measure~$\bar{\mu}:\events'\rightarrow\mathscr{I}$
could be, we introduce a notation of core.

@@

In the rest of the letter, we will provide examples of quantum interval-valued
probability measures on $\events_{24}$, and show how a quantum interval-valued
probability measure~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$
could be depending on different intervals~$\mathscr{I}$.

First, based on a Born rule probability measure, say $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$,
it is easy to construct a quantum interval-valued probability measure
$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$ whose unique core
element is $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$. Let $\circ$ denote
function composition.

>>>>

On one hand, the Kochen-Specker theorem is equivalent to non-existence
of quantum cryptodeterministic measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\} $,
where $\events$ is the set of all projections on a Hilbert space.
On the other hand, if we replace the range by the interval~$\left[0,1\right]$,
Gleason's theorem asserts that every quantum real-valued probability
measure~$\mu:\events\rightarrow\left[0,1\right]$ can be induced
by a density matrix according to the Born rule. These two extreme
cases can be understood in a broader framework of quantum interval-valued
probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$, where
$\mathscr{I}$ is a collection of intervals containing in $\left[0,1\right]$.
When we pick $\mathscr{I}$ as $\left\{ \imposs,\necess\right\} $,
where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$,
there is no quantum interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
by corollary~\ref{cor:Kochen-Specker-IVPM} of the Kochen-Specker
theorem. When the collection of intervals is $\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$,
a quantum interval-valued probability measure is well-behaved as a
usual quantum real-valued probability measure does.

Given any sub-event space~$\events'\subseteq\events$, in order to
qualify how well-behaved a quantum interval-valued probability measure~$\bar{\mu}:\events'\rightarrow\mathscr{I}$
could be, we introduce the notion of core.

@@

\noindent Then, Gleason's theorem guarantees that when $\bar{\mu}$
has an unique core element for any $\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$.
In the rest of the letter, we will provide examples of quantum interval-valued
probability measures on $\events_{24}$, and show how a quantum interval-valued
probability measure~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$
could be depending on different intervals~$\mathscr{I}$.

First, based on a Born rule probability measure, say $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$,
it is easy to construct a quantum interval-valued probability measure
$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$ whose unique core
element is $\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}$. For example, when
$\mathscr{I}$ is $\left\{ \imposs,\necess,\left[\frac{1}{4},\frac{1}{4}\right],\left[\frac{1}{2},\frac{1}{2}\right],\left[\frac{3}{4},\frac{3}{4}\right]\right\} $,
we have $\iota_{\infty}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}:\events_{24}\rightarrow\mathscr{I}$
and $\mathrm{core}\left(\iota_{\infty}\circ\mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right)=\left\{ \mu_{\ket{0}}^{\mathrm{\mathrm{B}}}\right\} $,
where $\iota_{\infty}\left(x\right)=\left[x,x\right]$ and $\circ$
denote function composition. This provides an example that even if
the
